---
title: "DSCI_601_M12_Lab_Cody_York"
author: "Cody York"
date: "2022-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports and Setup

```{r}
library(gtools)
library(tidyverse)
library(ggplot2)
library(dslabs)
```

## Creating a Deck of Cards

The below code will create a deck of cards to be used with the probability functions.

```{r}
suits <- c("Diamonds", "Clubs", "Hearts", "Spades")
numbers <- c("Ace", "Duece", "Three", "Four", "Five", "Six", "Seven", "Eight",
             "Nine", "Ten", "Jack", "Queen", "King")
deck <- expand.grid(number = numbers, suit = suits)
deck <- paste(deck$number, deck$suit)
```

## Calulate the Probability of a Natural 21 in Blackjack
  1. The code will first create a hand of 2 random cards from the deck using
permutations. Then two variables will be created for each card in the hand.
  2. The code will then define a "ten-card" or a ace.
  3. The code will then check to see if the first card in the hand is either an        ace or a "Ten-card".
  4. The code will then check to see if the second card in the hand is either an       ace or a "Ten-card".
  5. Then the probability will be calculated for getting a natural 21 in               blackjack.
```{r}

hands <- permutations(52, 2, v = deck)


ten_card <- c(paste("King", suits), paste("Queen", suits), paste("Jack", suits),
              paste("Ten", suits))
ace_card <- paste("Ace", suits)

first_card <- hands[, 1]
first_card_ten_card <- first_card %in% ten_card
first_card_ace_card <- first_card %in% ace_card

second_card <- hands[, 2]
second_card_ten_card <- second_card %in% ten_card
second_card_ace_card <- second_card %in% ace_card

natural_21_hands <- sum(first_card_ten_card, second_card_ace_card) +
  sum(first_card_ace_card, second_card_ten_card)

probability_natural_21 <- natural_21_hands / length(hands)
probability_natural_21
```

## Suppose widgits produced at Acme Widgit Works have probability 0.005 of being defective. Suppose widgits are shipped in cartons containing 25 widgits. What is the probability that a randomly chosen carton contains no more than one defective widgit?

  1. The distribution we need to use here is the Binomial Distribution. This
means we need the Bernoulli distribution probability p and the n number of         trials.
  2. First we will define a variable for the size of each crate which according        to the problem is 25.
  3. Next we will define the probability of defectiveness which as described in        the problem is 0.005
  4. Now, we will define a variable for the number of defective which in this            case is 1.
  5. Finally, we will use the dbinom function to get the probability.

```{r}

size_of_crate <- 25
probability_of_defective <- 0.005
defective_widgets_allowed <- 1

probability_of_widgets <- dbinom(x = defective_widgets_allowed,
                                 size = size_of_crate,
                                 prob = probability_of_defective)
probability_of_widgets

```

## If we pick 800 males at random, what is the distribution of the tallest person?  How rare is a seven footer in a group of 800 males?

  1. First we will create a data set from the heights data that has 800 males.
  2. Next, we will create a histogram graph of the heights using ggplot2. WE can         see that this is a normal distribution.
  3. Next we convert 7 foot to inches since the data is in inches.
  4. Next we will find the probability of males greater than 7 foot in these 800         records. For this we will find the number greater than 7 foot divided by         800. Currently there are 4 greater than 7 feet in this data set which           means there is a 0.5% chance of being taller than 7 feet.

```{r}
height_males <- heights %>%
  filter(sex == "Male") %>%
  pull(height)
height_800_males <- head(height_males, 800)

ggplot(as.data.frame(height_800_males), aes(x = height_800_males)) +
  geom_histogram(binwidth = 1, fill = "white", color = "black") +
  geom_vline(aes(xintercept = mean(height_800_males)), color = "red",
             linetype = "dashed") +
  labs(title = "Height Histogram Plot for 800 Males",
       x = "Height(inches)", y = "Count") +
  theme_dark()

target_height <- 80
height_800_males_7_foot <- height_800_males[height_800_males >= target_height]
probability_taller_than_7_foot <- length(height_800_males_7_foot) / 800
print(probability_taller_than_7_foot)
```